Figure: the scatterblob

### 2022-04-01 R/roles_table.Rmd
Got tables and table references working with manubot

---
knit: (function(input_file, encoding) {
  out_dir <- '../content';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '10.roles_table.md'))})
output: 
  md_document:
    variant: gfm #for debugging, forces table to be markdown, not html
    # variant: markdown
---

@@

Test citation of the above table @tbl:roles

>>>>

---
knit: (function(input_file, encoding) {
  out_dir <- '../content';
  rmarkdown::render(input_file,
 encoding=encoding,
 output_file=file.path(dirname(input_file), out_dir, '10.roles_table.md'))})
output: 
  md_document:
    variant: gfm #forces table to be markdown, not html
---

@@

<!-- An example citation of this table (Table @tbl:roles). -->
